 Quantile Regression Analysis for Statin Effects on Body mass Index

### 2021-04-17 manuscript/manuscript2.Rmd
update

base_box_plot

@@

```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using quadratic terms ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "newfig.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "newfig.png"))
```
 So,

@@

Marginal quadratic cholesterol effect

```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of the quadratic cholestrol effect on BMI leveles for four different quantiles of the conditional BMI distribution.  The ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "Total_chol_poly.png"))) {
    source(here::here("ci_splin.R"))
}
knitr::include_graphics(here::here("images", "Total_chol_poly.png"))
```

Splines modeling

```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of marginal cholestrol effect modeled as B splines.  The ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "TC_splin")))  
knitr::include_graphics(here::here("images", "TC_splin.png"))
```

@@

 tota people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL. Moreover,

>>>>

@@

```{r resu1, out.width = "100%", fig.align = "center", fig.cap = "Quantile regression of BMI ploted f for fifferent marginal effects. The predictors modeled using quadratic terms ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "newfig.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "newfig.png"))
```

@@

```{r resu4, out.width = "80%", fig.align = "center", fig.cap = "Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled as  quadratic .", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "Total_chol_poly.png"))) {
    source(here::here("ci_splin.R"))
}
knitr::include_graphics(here::here("images", "Total_chol_poly.png"))
```

```{r resu330, out.width = "80%", fig.align = "center", fig.cap = " Illustration of a 90th quantile regression of the BMI. The cholesterol term modeled  as B splines. ", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "TC_splin")))  
knitr::include_graphics(here::here("images", "TC_splin.png"))
```

@@

 total people who have TC levels around 190 mg/dL have the lowest fasting glucose levels for the lowest quantile, for the second quantile optimal cholesterol level is around 220mg/dL, and for the upper quantile, the optimal cholesterol level is around 200 mg/dL. Moreover,
